\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{longtable} % For handling long project lists if needed

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}

% Reduce list spacing
\setlist[itemize]{leftmargin=*, labelsep=5mm, topsep=2pt, itemsep=1pt}

\begin{document}

% Header
\begin{center}
    {\LARGE\bfseries Mohamed Ameen} \\[6pt]
    {\large Engineering Leader \& Unity, Georgia Institute of Technology} \\[8pt]
    Heilbronn, Baden-Württemberg, Germany \\[4pt]
    \href{https://www.linkedin.com/in/mohamedameen93/}{\texttt{www.linkedin.com/in/mohamedameen93}} \\[4pt]
    \textit{Affiliated with Unity and Georgia Institute of Technology} \\[4pt]
    13K followers $\;\bullet\;$ 500+ connections
\end{center}

\vspace{12pt}

\section*{Professional Profile}

\begin{itemize}
    \item Engineering leader with a \textbf{decade-long experience} delivering production-grade software.
    \item Currently affiliated with \textbf{Unity} (industry) and \textbf{Georgia Institute of Technology} (academic).
    \item Based in \textbf{Heilbronn, Baden-Württemberg, Germany}.
    \item Active LinkedIn presence with \textbf{13K followers} and \textbf{500+ professional connections}.
\end{itemize}

\section*{Courses \& Technical Competencies}
\begin{itemize}
    \item Advanced Competitive Strategy
    \item Analog \& Digital Electronics Course
    \item Broadband Technologies Seminar
    \item CS50: Introduction to Computer Science
    \item Career Development and Soft Skills Workshop
    \item Certified Marketing Consulting Program
    \item Competitive Strategy
    \item Developing Innovative Ideas for New Companies: The First Step in Entrepreneurship
    \item Embedded Hardware and Operating Systems
    \item Embedded Systems Diploma
    \item Entrepreneurship Camp
    \item Entrepreneurship Fundamentals
    \item Foundations of Business Strategy
    \item Foundations of Programming - Fundamentals
    \item Fundamental Entrepreneurial Concepts for Startup Ventures
    \item Fundamentals of Software Version Control
    \item Gamification
    \item Grow to Greatness: Smart Growth for Private Businesses, Part I
    \item Grow to Greatness: Smart Growth for Private Businesses, Part II
    \item How to Build a Startup
    \item Innovation for Entrepreneurs: From Idea to Marketplace
    \item Introduction to Marketing
    \item Introduction to Power Electronics
    \item Introduction to RTOS
    \item Leading with Emotional Intelligence
    \item Machine Learning (CS 7641)
    \item Marketing for Entrepreneurs
    \item New Venture Finance: Startup Funding for Entrepreneurs
    \item Personal Branding Basics
    \item Programmable Logic Controller - PLC
    \item RTOS Architecture Porting to ARM Cortex-M4
    \item SCADA \& LabView Course
    \item The Entrepreneur's Toolkit
\end{itemize}

\section*{Projects}
\begin{description}
    \item[A Benchmark of Supervised Learning Algorithms] Benchmarks five supervised learning algorithms on real-world classification problems. \href{https://github.com/mohamedameen93/A-Benchmark-of-Supervised-Learning-Algorithms}{GitHub}
    \item[vCPU Scheduler and Memory Coordinator] Dynamically handles memory utilization and manages resources for virtual machines on Ubuntu OS.
    \item[An Autonomous Vehicle System For Udacity's Carla] Implements ROS nodes for traffic light detection, vehicle control, and waypoint following on Carla (Udacity’s Self-Driving Lincoln MKZ). \href{https://github.com/mohamedameen93/An-Autonomous-Vehicle-System-For-Carla}{GitHub}
    \item[Semantic Segmentation using Fully Convolutional Networks] Builds a fully convolutional neural network based on VGGNet-16 for semantic segmentation of drivable surface areas from vehicle dashboard camera video. \href{https://github.com/mohamedameen93/Semantic-Segmentation-using-Fully-Convolutional-Networks}{GitHub}
    \item[Vehicle Path Planning Algorithm] Designs a path planning algorithm to navigate a car around a simulated highway with traffic, waypoints, telemetry, and sensor fusion data. \href{https://github.com/mohamedameen93/Vehicle-Path-Planning-Algorithm}{GitHub}
    \item[Moving object state estimation using Unscented Kalman Filter] Uses an unscented filter to estimate the state of a moving object with noisy LIDAR and radar measurements. \href{https://github.com/mohamedameen93/Sensor-Fusion-Using-Unscented-Kalman-Filter}{GitHub}
    \item[Vehicle Steering Using Model Predictive Control] Implements Model Predictive Control in C++ to drive a vehicle around a simulator track. \href{https://github.com/mohamedameen93/Vehicle-Steering-Using-Model-Predictive-Control}{GitHub}
    \item[Vehicle Localization Using Particle Filters] Implements a 2D particle filter in C++ to localize a vehicle using a map and initial localization data. \href{https://github.com/mohamedameen93/Vehicle-Localization-Using-Particle-Filters}{GitHub}
    \item[Moving object state estimation using Extended Kalman Filter] Uses a Kalman filter to estimate the state of a moving object with noisy LIDAR and radar measurements. \href{https://github.com/mohamedameen93/Extended-Kalman-Filter}{GitHub}
    \item[Vehicle Detection and Tracking] Builds a software pipeline to detect vehicles in video, including data loading, feature extraction, classification, and video processing. \href{https://github.com/mohamedameen93/Vehicle-Detection-and-Tracking}{GitHub}
    \item[Advanced Lane Finding Using OpenCV] Uses OpenCV to identify lane boundaries in video from a front-facing vehicle camera, including camera calibration, distortion correction, and lane curvature estimation. \href{https://github.com/mohamedameen93/Advanced-Lane-Finding-Using-OpenCV}{GitHub}
    \item[Behavioral Cloning | End to End Learning for Self Driving Cars] Uses a Keras deep neural network to clone car driving behavior using data from Udacity’s Self-Driving Car Simulator (based on NVIDIA’s End-to-End Learning paper). \href{https://github.com/mohamedameen93/Behavioral-Cloning-End-to-End-Learning-for-Self-Driving-Cars}{GitHub}
    \item[German Traffic Sign Classification Using TensorFlow] Classifies images from the German Traffic Sign Dataset (50,000+ images, 43 classes) using VGGNet, achieving 97.6\% testing accuracy. \href{https://github.com/mohamedameen93/German-Traffic-Sign-Classification-Using-TensorFlow}{GitHub}
    \item[Lane Lines Detection Using Python and OpenCV] Detects lane lines in images and video using Python and OpenCV, focusing on straight lines. \href{https://github.com/mohamedameen93/Lane-lines-detection-using-Python-and-OpenCV}{GitHub}
    \item[Little Box Challenge | Micro-Inverter project] Builds a high-power-density micro-inverter (50W/in³) for the Google/IEEE Little Box Challenge using design analysis, simulation, SPICE, and embedded programming. \href{https://littleboxchallenge.com}{Website}
    \item[PV System with Pure Sine Wave Inverter] Implements a residential PV system with a pure sine wave inverter using a DC boost converter, microcontroller, H-bridge, and LC filter with SPWM switching.
    \item[Vehicle Steering Using PID Control] Implements a PID controller to steer a vehicle around a track in Udacity’s Simulator. \href{https://github.com/mohamedameen93/Vehicle-Steering-Using-PID-Control}{GitHub}
\end{description}

\section*{Test Scores}
\begin{itemize}
    \item \textbf{TOEFL Test} \\
          Total Score: \textbf{109} (Reading: 29, Listening: 28, Speaking: 26, Writing: 26)
\end{itemize}

\section*{Languages}
\begin{itemize}
    \item \textbf{Arabic} \hfill Native or bilingual proficiency
    \item \textbf{English} \hfill Native or bilingual proficiency
    \item \textbf{German} \hfill (Proficiency level available upon request)
\end{itemize}

\section*{Accomplishments}
\begin{itemize}
    \item Participated in the IEEE/Google Little Box Challenge with a high-power-density micro-inverter prototype.
    \item Achieved \textbf{97.6\% testing accuracy} in German Traffic Sign Classification using VGGNet.
\end{itemize}

\section*{LinkedIn Profile}
\href{https://www.linkedin.com/in/mohamedameen93/}{https://www.linkedin.com/in/mohamedameen93/}

\vspace{12pt}

{\footnotesize \textit{This document is generated from publicly available LinkedIn profile data as of October 30, 2025. Full work experience, education, skills, and certifications are accessible via the LinkedIn profile.}}

\end{document}